\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-08 paper/main.tex
update in-text VMware reference
WIP updates to onion comment section

At another extreme, virtual machines~\citep{Gold74, AltiEtal05,
  vmware} provide a hardware-level simulation of the desired system.
Virtual machines are typically isolated from the user's system, such
that installing or running software on a virtual machine does not
impact the user's primary operating system or computing environment.
Containers~\citep[e.g.,][]{Merk14, KurtEtal17} provide a similar
``isolated'' experience.  Although containerized environments do not
specify hardware-level operations, they are typically packaged with a
complete operating system, in addition to a complete copy of Python
and any relevant package dependencies.  Virtual
environments~\citep[e.g.,][]{vanREtal14} also provide a computing
environment that is largely separated from the user's main
environment.  They incorporate a copy of Python and the target
software's dependencies, but virtual environments do not specify or
reproduce an operating system for the runtime environment.  Each of
these systems (virtual machines, containers, and virtual environments)
guarantees (to differing degrees-- at the hardware level, operating
system level, and Python environment level, respectively) that the
relevant code will run similarly for different users.  However, each
of these systems also relies on additional software that can be
resource intensive or burdensome to install or configure.

@@

\subsection{Software functionalities}%\label{sec:functionalities}

@@

\subsubsection{The onion comment}\label{subsec:onion}
For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the \textit{onion comment}. An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, how it should be installed. Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages via \texttt{davos} intuitive and familiar. To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to install the package as desired manually via the command line (see Fig.~\ref{fig:snippet1}).

@@

@@

\subsubsection{The \texttt{davos} config}

>>>>

At another extreme, virtual machines~\citep{Gold74, AltiEtal05,
  Rose99} provide a hardware-level simulation of the desired system.
Virtual machines are typically isolated from the user's system, such
that installing or running software on a virtual machine does not
impact the user's primary operating system or computing environment.
Containers~\citep[e.g.,][]{Merk14, KurtEtal17} provide a similar
``isolated'' experience.  Although containerized environments do not
specify hardware-level operations, they are typically packaged with a
complete operating system, in addition to a complete copy of Python
and any relevant package dependencies.  Virtual
environments~\citep[e.g.,][]{vanREtal14} also provide a computing
environment that is largely separated from the user's main
environment.  They incorporate a copy of Python and the target
software's dependencies, but virtual environments do not specify or
reproduce an operating system for the runtime environment.  Each of
these systems (virtual machines, containers, and virtual environments)
guarantees (to differing degrees-- at the hardware level, operating
system level, and Python environment level, respectively) that the
relevant code will run similarly for different users.  However, each
of these systems also relies on additional software that can be
resource intensive or burdensome to install or configure.

@@

\subsection{Software functionalities}

@@

\subsubsection{The onion comment}\label{subsec:onion}
For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the \textit{onion comment}. An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, how it should be installed. Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar. To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to install the package as desired manually via the command line (see Fig.~\ref{fig:snippet1}).
%Figure \ref{fig:snippet1} provides a number of examples of \texttt{smuggle} statements accompanied by

@@

Onion comments are also useful for smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; see Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_ for examples). However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}. If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will search for the smuggled package in the local environment (as usual), and if it is found, further check whether the existing version satisfies the given constraint(s). If either check fails, \texttt{davos} will install and use a suitable version of the package (see Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_ for examples).

@@

\subsubsection{The \texttt{davos} config}\label{subsec:config}
